---
title: "Learned Attentional Flexibility"
output: flex_html_notebook
---

First load in the necessary packages and seed the random number generator
```{r}
library(ggplot2)
library(matlabr)
library(tidyr)
library(ez)
library(plyr)
options(matlab.path = "C:/Program Files/MATLAB/R2014b.app")
set.seed(400)
```

set the installation directory here
```{r}
dir="C:/Users/aws27/Documents/Flex01_Manuscript/AttentionalFlexibility"
```

First we'll analyze the behavioral RT data.
Start by getting in the correct directory and then generate the behavioral summary files RTs.txt and Accuracies.txt. This requires a matlab installation.


```{r}
setwd(paste(dir, "/Programs", sep=""))
run_matlab_script("AnalyzeFlex01AttnTask.m", verbose = TRUE, desktop = FALSE, splash = FALSE, display = FALSE, wait = TRUE)
```

```{r}
setwd(paste(dir, "/OutputFiles", sep=""))
dfRT <- read.table("RTs.txt",header=TRUE)
dfAcc <- read.table("Accuracies.txt",header=TRUE)
```

Reorganize the data in preparation for the ANOVA and then run an ANOVA on RTs and on Accuracy


```{r}
dfRT_long <- gather(dfRT,condition, measurement, HoldMH:ShiftMS,factor_key=TRUE)
dfAcc_long <- gather(dfAcc,condition, measurement, HoldMH:ShiftMS,factor_key=TRUE)

dfRT_long=cbind(Cue=rep(c("Hold","Shift"),each=23),dfRT_long)
dfAcc_long=cbind(Cue=rep(c("Hold","Shift"),each=23),dfAcc_long)
dfRT_long=cbind(Ctx=rep(c("25%Shift","50%Shift","75%Shift"),each=46),dfRT_long)
dfAcc_long=cbind(Ctx=rep(c("25%Shift","50%Shift","75%Shift"),each=46),dfAcc_long)
RT_Anova = ezANOVA(data=dfRT_long,dv=measurement,wid=SubID,within = .(Cue,Ctx))
Acc_Anova = ezANOVA(data=dfAcc_long,dv=measurement,wid=SubID,within = .(Cue,Ctx))
```

Print results for RT ANOVA

```{r}
RT_Anova
```


Now print results for Accuracy ANOVA

```{r}
Acc_Anova
```

Now get the cell means and SE to graph the RT and Accuracy data using ggplot2

```{r}
RTOut=ddply(dfRT_long, c("Cue", "Ctx"), summarise, mean = mean(measurement), sd = sd(measurement), sem = sd(measurement)/sqrt(length(measurement)))
AccOut=ddply(dfAcc_long, c("Cue", "Ctx"), summarise, mean = mean(measurement), sd = sd(measurement), sem = sd(measurement)/sqrt(length(measurement)))

ggplot(data=RTOut, aes(x=Ctx,y=mean,fill=Cue)) + geom_bar(stat="identity", color="black", width=0.5, size=1, position = position_dodge()) + theme_classic() + theme(axis.line = element_line(colour = 'black', size = 1.5), axis.ticks = element_line(colour = "black", size = 1.5)) + labs(x="Attention Shift Probability", y="Response Time (ms)", fill="") + coord_cartesian(ylim=c(900, 1150)) + scale_fill_manual(values=c('#BFBFBF','#FFFFFF')) + theme(text = element_text(size=20)) + geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2, size=1, position=position_dodge(.5)) + scale_x_discrete(breaks=c("25%Shift","50%Shift","75%Shift"),labels=c("25% Shift", "50% Shift", "75% Shift"))

ggplot(data=AccOut, aes(x=Ctx,y=mean,fill=Cue)) + geom_bar(stat="identity", color="black", width=0.5, size=1, position = position_dodge()) + theme_classic() + theme(axis.line = element_line(colour = 'black', size = 1.5), axis.ticks = element_line(colour = "black", size = 1.5)) + labs(x="Attention Shift Probability", y="Behavioral Accuracy (%)", fill="") + coord_cartesian(ylim=c(85, 100)) + scale_fill_manual(values=c('#BFBFBF','#FFFFFF')) + theme(text = element_text(size=20)) + geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2, size=1, position=position_dodge(.5))+ scale_x_discrete(breaks=c("25%Shift","50%Shift","75%Shift"),labels=c("25% Shift", "50% Shift", "75% Shift"))
```


Now run the RL model (again in matlab)

```{r}
setwd(paste(dir, "/Programs", sep=""))
run_matlab_script("RLmodel_final.m", verbose = TRUE, desktop = FALSE, splash = FALSE, display = FALSE, wait = TRUE)
```

Get mean and std of alpha rates

```{r}
setwd(paste(dir, "/OutputFiles", sep=""))
dfAlpha <- read.table("Alphas.txt",header=TRUE)
dfAlpha=cbind(sub=c("sub"),dfAlpha)
mean(dfAlpha[["Alpha"]])
sd(dfAlpha[["Alpha"]])
```


Rerun with the subject with a negative fit excluded.

```{r}
setwd(paste(dir, "/Programs", sep=""))
run_matlab_script("RLmodel_exclusion.m", verbose = TRUE, desktop = FALSE, splash = FALSE, display = FALSE, wait = TRUE)
```

Read in the alpha rate data and plot them.

```{r}
setwd(paste(dir, "/OutputFiles", sep=""))
dfAlpha <- read.table("Alphas.txt",header=TRUE)
dfAlpha=cbind(sub=c("sub"),dfAlpha)

ggplot(dfAlpha, aes(x=sub, y=Alpha)) + geom_jitter(position = position_jitter(width = 0.05, height = 0), size=4, shape=21, stroke=2) + theme_classic() + theme(axis.line = element_line(colour = 'black', size = 1.5), axis.ticks = element_line(colour = "black", size = 1.5)) + labs(x="", y="Learning Rate (alpha)", fill="") + theme(text = element_text(size=20))
```

Get mean and std of alpha rates

```{r}
mean(dfAlpha[["Alpha"]])
sd(dfAlpha[["Alpha"]])
```

Compute the behavioral learning score for each participant and correlate this with the fit t stat.

```{r}
dfRT2 <- dfRT[-c(6), ]
rownames(dfRT2) <- seq(length=nrow(dfRT2))
dfAlpha$Learn<- (dfRT2[["ShiftMH"]]-dfRT2[["HoldMH"]])-(dfRT2[["ShiftMS"]]-dfRT2[["HoldMS"]])
cor.test(dfAlpha[["Fit"]],dfAlpha[["Learn"]])
```

Now make a scatter plot of Fits and Learning Scores

```{r}
ggplot(dfAlpha, aes(x=Fit, y=Learn)) + geom_point(size=4, shape=21, stroke=2) + theme_classic() + theme(axis.line = element_line(colour = 'black', size = 1.5), axis.ticks = element_line(colour = "black", size = 1.5)) + labs(x="PE Model Fit t-Statistic", y="Flexibility Learning Score (ms)", fill="") + theme(text = element_text(size=20)) + geom_smooth(method=lm, se=FALSE,colour="black",linetype="dashed") 
```


Run the behavioral analysis of the model training task and give the relevant descriptive statistics

```{r}
setwd(paste(dir, "/Programs", sep=""))
run_matlab_script("AnalyzeMapTask.m", verbose = TRUE, desktop = FALSE, splash = FALSE, display = FALSE, wait = TRUE)
setwd(paste(dir, "/OutputFiles", sep=""))
dfMap <- read.table("MapTask.txt",header=TRUE)
range(dfMap[["Hits"]])
mean(dfMap[["Hits"]])
sd(dfMap[["Hits"]])
mean(dfMap[["FalseAlarm"]])
sd(dfMap[["FalseAlarm"]])
```

Generate the stimulus timing files for MRI analysis in FSL

```{r}
setwd(paste(dir, "/Programs", sep=""))
run_matlab_script("FactorialGLM_GetTimes_Paper.m", verbose = TRUE, desktop = FALSE, splash = FALSE, display = FALSE, wait = TRUE)
run_matlab_script("RL_GetTimes_Paper.m", verbose = TRUE, desktop = FALSE, splash = FALSE, display = FALSE, wait = TRUE)
```